---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Phase2.2CATE

<!-- badges: start -->
<!-- badges: end -->

The goal of Phase2.2CATE is to perform Federated Adaptive Causal Estimation of Conditional Vaccine Effect.

## Installation

This package should be run locally (i.e. NOT on docker). You can install the development version of Phase2.2CATE like so:

```{r load, eval = F}
remotes::install_github('clara-lea/Phase2.2CATE')
```

## Running the analysis

These are the lines of code to run CATE

```{r run, eval = F}
library(Phase2.2CATE)
input.path = "" #specify the path to the folder containing 2.2 data
output.path = "" #specify where you would like the results to be saved
siteid = "" #specify siteid

run_analysis(input.path, output.path, siteid)
```

After running the analysis, please send the result file directly to Clara-Lea.


